\plaintitle

### 2016-09-19 drafts/labor/piecework_lit.tex

\documentclass[trackingWork]{subfiles}

% \renewcommand{\topic}[1]{#1}

\makeatletter
\makeatother
\begin{document}
\section{A Review of Piecework}
\topic{The HCI community has used the term ``piecework'' to describe
myriad instantiations of on--demand labor,
but this reference has generally been offered in passing.}
As this paper principally traces a relationship between
the historical piecework and the contemporary crowd work
(or on--demand labor more generally),
this casual familiarity with piecework may prove insufficient.
We'll more carefully discuss piecework in this section in order
to inform the the rest of the argument.
Specifically, we will
\begin{inlinelist}
  \item define ``piecework'' as researchers in the topic understood it;
  \item trace the rise of piecework at a very high level,
        identifying key figures and ideas during this time; and finally
  \item look at the fall of piecework, such as it was,
        considering in particular
        the factors that may have led to piecework's
        eventual demise \msb{did it demise? there are sweatshops around the world today}.
\end{inlinelist}

\subsection{What was piecework?}
\topic{Aligning on--demand work with piecework requires an understanding of what piecework is. While ``piecework'' has had multiple definitions over time,
we can trace a constellation of characteristics that recur throughout the literature.}
We will follow this history of research, collecting
descriptions,
examples, and
provided definitions of piecework, trying
to trace the outline of a working understanding of
\textit{what piecework is}.

@@

@@

@@

\topic{As increasing attention revealed problems in piecework as it related to workers,
workers themselves began to speak out about their frustration with this new regime.}
It began, arguably, with \citeauthor{riisOtherSideLives}'s photo--documentary work,
but this led to industry organizations representing
railway workers, mechanical engineers, and others contributing their perspectives
\cite{american1921problem,richards1904anything,riisOtherSideLives}.
%Nevertheless, piecework continued to permeate low--skilled labor.
% \topic{Necessity drove the widespread adoption of piecework and work decomposition%
% , perhaps more even than Ford's assembly line.}
%\topic{Despite the intense growth of the piecework approach to renumeration,
%this time was not without turmoil.}
%These worker organizations weighed in on
%(or, more precisely, against) piecework and the myriad oversights it made in valuing workers' time
%\cite{american1921problem,richards1904anything}.
For example, \citeauthor{10.2307/3827491} describes worker resistance among a largely disempowered community --- young women employed by piecework
\cite{10.2307/3827491}.

@@

\topic{However, piecework's popularity in the United States and Europe plummeted almost as quickly as it had climbed.}
\citeauthor{hart2013rise}'s work substantively explores the precipitous decline of piecework in the last third of the \nth{20} century.
In their work, \citeauthor{hart2013rise} offer a number of explanations for the sudden vanishing of piecework.
The salient suggestions include:
\begin{inlinelist}
\item the emergence of more effective, more nuanced incentive models
--- rewarding teams for complex achievements, for instance;
\item the shifting of these industries (manufacturing, clothing, etc\dots)
to other countries;
\item the quality of ``multidimensional'' work becoming too difficult to evaluate.
\end{inlinelist}
\cite{hart2013rise}.
% the gendered and stratified dynamics at play in the matchgirls strike

% \topic{Piecework declined in popularity in the United States, but
% its spirit thrived through the mid--\nth{20} century in
% scientific management and Fordism.}
% Concurrent with the fall of piecework was arguably the rise of factories as centers of work.

\subsection{From piecework to on--demand work}
Crowd work and gig work are fundamentally an instantion of piecework.
First, workers on platforms such as Mechanical Turk and Uber are generally incentivized by unit of work, even if some may be offered an hourly base salary as well.
Second, workers are attracted to these platforms by the freedom they offer to pick the time and place of work~\cite{martin2014being,whyWouldAnyoneBrewer}.
Third, system developers as on Mechanical Turk typically assume no professional skills in transcription or other areas, and attempt to build that expertise into the workflow~\cite{noronha2011platemate,bernsteinSoylent}.

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\makeatother
\begin{document}

\section{A Review of Piecework}

\topic{The HCI community has used the term ``piecework'' to describe
myriad instantiations of on--demand labor,
but this reference has generally been offered in passing.}
As this paper principally traces a relationship between
the historical piecework and the contemporary crowd work
(or on--demand labor more generally),
this casual familiarity with piecework may prove insufficient.
We'll more carefully discuss piecework in this section in order
to inform the the rest of the argument.
Specifically, we will
\begin{inlinelist}
  \item define ``piecework'' as researchers in the topic understood it;
  \item trace the rise of piecework at a very high level,
        identifying key figures and ideas during this time; and finally
  \item look at the fall of piecework, such as it was,
        considering in particular
        the factors that may have led to piecework's
        eventual demise \msb{did it demise? there are sweatshops around the world today}.
\end{inlinelist}

\subsection{What was piecework?}

\topic{While ``piecework'' has proven difficult to concretize from the literature,
we can trace a constellation of characteristics of piece work that recur throughout the literature.}
% We'll follow the history of research, collecting
\topic{Aligning on--demand work with piecework requires an understanding of what piecework is. While ``piecework'' has had multiple definitions over time,
we can trace a constellation of characteristics that recur throughout the literature.}
We will follow this history of research, collecting
descriptions,
examples, and
provided definitions of piecework, trying
to trace the outline of a working understanding of
\textit{what piecework is}.

@@

\msb{After reading this paragraph, I don't know what it's supposed to be teaching me.
What I got out of it is that a bunch of people did piecework, but
I don't know why or in fact why these are different than the sources we cite earlier.
Can you hone it?}

\ali{I wanted that paragraph to be about the rising popularity and application of piecework
(especially as it approached its ``heyday'' (a la \cite{hart2013rise})),
coming from humble beginnings as it found its footing.
Given that intent\dots~

Should I \textbf{refactor} or \textbf{rewrite}?}

\topic{First applied to farm work, as
\citeauthor{hughRaynbirdTaskWork} and others illustrate,
the practice remained relatively obscure until
it was brought to the textile industry
\cite{hughRaynbirdTaskWork}.}
At the turn of the \nth{20} century,
when \citeauthor{riisOtherSideLives} was documenting abhorrent working \& living conditions of pieceworkers in New York City,
\citeauthor{norton1900textile} was providing substantive guidance on various wage regimes,

@@

\topic{As increasing attention revealed problems in piecework as it related to workers,
workers themselves began to speak out about their frustration with this new regime.}
It began, arguably, with \citeauthor{riisOtherSideLives}'s photo--documentary work,
but this led to industry organizations representing
railway workers, mechanical engineers, and others contributing their myriad perspectives
\cite{american1921problem,richards1904anything,riisOtherSideLives}.
Nevertheless, piecework continued to permeate low--skilled labor.

% \topic{Piecework became an important contributor to the war effort in the Second World War,

@@

\topic{Despite the intense growth of the piecework approach to renumeration,
this time was not without turmoil.}
As previously discussed, a number of worker organizations weighed in on
(or, more precisely, against) piecework and the myriad oversights it made in valuing workers' time
\cite{american1921problem,richards1904anything}.
\citeauthor{10.2307/3827491} describes worker resistance among a largely disempowered community --- young women employed by piecework
\topic{As increasing attention revealed problems in piecework as it related to workers,
workers themselves began to speak out about their frustration with this new regime.}
It began, arguably, with \citeauthor{riisOtherSideLives}'s photo--documentary work,
but this led to industry organizations representing
railway workers, mechanical engineers, and others contributing their perspectives
\cite{american1921problem,richards1904anything,riisOtherSideLives}.
%Nevertheless, piecework continued to permeate low--skilled labor.
% \topic{Necessity drove the widespread adoption of piecework and work decomposition%
% , perhaps more even than Ford's assembly line.}
%\topic{Despite the intense growth of the piecework approach to renumeration,
%this time was not without turmoil.}
%These worker organizations weighed in on
%(or, more precisely, against) piecework and the myriad oversights it made in valuing workers' time
%\cite{american1921problem,richards1904anything}.
For example, \citeauthor{10.2307/3827491} describes worker resistance among a largely disempowered community --- young women employed by piecework
\cite{10.2307/3827491}.

@@

\topic{However, piecework's popularity in the United States and Europe plummeted almost as quickly as it had climbed.}
\citeauthor{hart2013rise}'s work substantively explores the precipitous decline of piecework in the last third of the \nth{20} century.
In their work, \citeauthor{hart2013rise} offer a number of explanations for the sudden vanishing of piecework.
The salient suggestions include:
\begin{inlinelist}
\item the emergence of more effective, more nuanced incentive models
--- rewarding teams for complex achievements, for instance;
\item the shifting of these industries (manufacturing, clothing, etc\dots)
to other countries;
\item the quality of ``multidimensional'' work becoming too difficult to evaluate.
\end{inlinelist}
\cite{hart2013rise}.

\subsection{Why is piecework relevant to crowdwork?}

\msb{I assume this is forthcoming?}
Using the definition of piecework that we came up with earlier, we argue that
crowd work is fundamentally an instantiation of piecework, and
that we can more precisely anticipate the answers to the open research questions we discussed earlier.
We'll show that the dimensions of crowd work that the broader HCI community has been studying
align with the history of piecework, and that this can greatly inform predictions about the future of crowd work.
\subsection{From piecework to on--demand work}
Crowd work and gig work are fundamentally an instantion of piecework.
First, workers on platforms such as Mechanical Turk and Uber are generally incentivized by unit of work, even if some may be offered an hourly base salary as well.
Second, workers are attracted to these platforms by the freedom they offer to pick the time and place of work~\cite{martin2014being,whyWouldAnyoneBrewer}.
Third, system developers as on Mechanical Turk typically assume no professional skills in transcription or other areas, and attempt to build that expertise into the workflow~\cite{noronha2011platemate,bernsteinSoylent}.
